\section{Projects}
\begin{experience}{\href{https://deminifyjs.netlify.app/}{\textbf{Deobfuskate}}}{
	% \position{Deobfuskate}{}{}
}
A web app for "decrypting" minified / obfuscated javascript source files.
It performs a bunch of operations to make the obfuscated code readable.
It can be useful for reverse engineering.
\begin{itemize}
	\item Source code beautifier / syntax highlighter.
	\item Variable Renaming.
	\item Eval, Array Unpacking.
	\item Proxy function removal.
	\item Expression Simplification.
\end{itemize}
\end{experience}

\begin{experience}{\href{http://whoproduced.herokuapp.com}{\textbf{WhoProduced}}}{
		% \position{c}{}{}
}
WhoProduced is a website and app database of producer credits.
Uses the Genius api to retrieve producer credits.
Uses the spotify api to fetch information abount songs, artistes, and albums.

\end{experience}

\begin{experience}{\href{https://github.com/foderking/Minimal-React-Template.git}{\textbf{Minimal React Template}}}{
		% \position{}{}{}
}
A free, clean and minimalist template for building react apps that can kickstart development.
Uses yarn for package management, parcel for bundling, and react boostrap for UI.

\end{experience}


\begin{experience}{\href{https://light-chess.netlify.app/}{\textbf{Light-Chess}}}{
	% \position{}{}{}
	%\position{Front-End Developer}{2011}{2013}
}
A lightweight chess app written from purely in react.
it uses no external dependencies, and does all move generation and validation itself

\end{experience}


\begin{experience}{\href{https://github.com/foderking/Friedfish}{\textbf{Friedfish}}}{
	% \position{}{}{}
	%\position{Front-End Developer}{2011}{2013}
}
A fast chess engine written in Nim.
It uses bitboards for board representation, and chess algorithms like negamax for search

\end{experience}


\begin{experience}{\href{https://github.com/foderking/ComicvineAPI}{\textbf{ComicvineAPI}}}{
	% \position{}{}{}
	%\position{Front-End Developer}{2011}{2013}
}
An unofficial API for the comicvine forum

\end{experience}



%\shortexperience[last]{Redimi}{\position{Java Programmer}{2010}{2011}}

